Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation \thanks{The research was supported by UBACyT20020170100428BA and the CLIMAX Project funded by Belmont Forum/ANR-15-JCL/-0002-01. Elio Campitelli was supported by a PhD grant from CONICET, Argentina.}

### 2021-08-12 analysis/paper/shceof.tex
Render

\begin{figure*}
\includegraphics{../figures/sst-psi-2-1} \caption{Regression maps of cEOF2 with SST (K, column a) and streamfunction zonal anomalies (\(m^2/s\times10^-7\), shaded) with their corresponding activity wave flux (vectors) (column b). Areas marked with dots have p-values smaller than 0.01 adjusted for FDR. \textcolor{red}{Agregar unidades. Quedaría mucho mejor el gráfico y creo que se prestaría a menos confusión si colocas las barras de colores en las columnas corrrespondientes. Otro detalle es que en gral. para el gráfico de streamfunction la escala de colores se usa al revés para que los azules (positivos) sean ciclónicos y los rojos anticiclónicos}}\label{fig:sst-psi-2}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics{../figures/sst-psi-2-1} \caption{Regression maps of cEOF2 with SST (K, column a) and streamfunction zonal anomalies (\(m^2/s\times10^-7\), shaded) with their corresponding activity wave flux (vectors) (column b). Areas marked with dots have p-values smaller than 0.01 adjusted for FDR.}\label{fig:sst-psi-2}
\end{figure*}
